\begin{abstract}
We study a concrete path toward verifiable reinforcement learning by focusing on a narrow, auditable setting: offline Deep Q-Network (DQN) training from a fixed trajectory dataset. Rather than addressing ``RL + ZK'' in full generality, we isolate a pipeline in which trajectories are first collected, then flattened into a fixed transition dataset, committed via a Merkle tree, and finally used for offline value learning. This setting naturally supports commitment, reproducibility, and proof-oriented statement design.

Experiments on CartPole-v1 show that dataset structure interacts strongly with the learning paradigm. On a narrow, high-return behavior dataset collected from a trained DQN policy with $\epsilon=0.10$, naive offline Double DQN performs poorly, with 100-episode re-evaluation ranging only from 31.50 to 94.68 across seeds. In contrast, behavior cloning on the same dataset is strong, reaching 392.87, 461.88, and 398.19 mean return over 100 evaluation episodes across three seeds. Conservative Q-Learning (CQL-lite) substantially improves over naive offline Double DQN in the same setting, reaching 416.14, 341.79, and 447.42 mean return.

Motivated by this setting, we implement a pre-ZK artifact-verifier prototype for the core computations that a future proof system would need to certify. The current prototype verifies membership of sampled transitions in a committed dataset, Double-DQN-style Bellman target correctness, SmoothL1 temporal-difference loss correctness, minibatch-average loss correctness, and public anchoring of the audited checkpoint via SHA-256. We further implement and benchmark a stronger one-step SGD update prototype that checks gradient recomputation consistency, parameter-delta consistency, SGD update consistency, and pre/post checkpoint anchoring on committed minibatches. Although the current system is not yet a full zero-knowledge proof of training, it already establishes the statement structure for committed-data membership, TD-arithmetic correctness, and one-step update consistency, thereby providing a concrete intermediate milestone toward verifiable offline RL training.
\end{abstract}

\begin{IEEEkeywords}
Offline reinforcement learning, deep Q-network, zero-knowledge proofs, verifiable machine learning, Merkle commitment, fixed-point arithmetic, temporal-difference learning.
\end{IEEEkeywords}