\appendices

\section{Hyperparameter Details}
\label{app:hyperparameters}

\Cref{tab:app-hparams} records the settings that were explicitly fixed and repeatedly referenced in the reported experiments.

\begin{table}[!t]
\centering
\footnotesize
\caption{Explicitly reported experimental settings.}
\label{tab:app-hparams}
\begin{tabular}{ll}
\toprule
Setting & Value \\
\midrule
Environment & CartPole-v1 \\
Observation dim. & 4 \\
Action space size & 2 \\
Network arch. & MLP, 2 hidden layers $\times$ 128 \\
Hidden activation & ReLU \\
Offline DQN LR & $1 \times 10^{-4}$ \\
CQL-lite LR & $1 \times 10^{-4}$ \\
TD loss & SmoothL1Loss (Huber) \\
Gradient clipping & 10.0 \\
Target network & Enabled \\
Target rule & Double DQN \\
CQL-lite $\alpha$ & 1.0 \\
Behavior policy & DQN, $\epsilon = 0.10$ \\
Model selection & 10-ep periodic eval \\
Final evaluation & 100-episode re-eval \\
Seeds & 42, 123, 999 \\
\bottomrule
\end{tabular}
\end{table}

\section{Dataset Summary}
\label{app:dataset-stats}

\Cref{tab:app-datasets} summarizes the four offline datasets used in this study. All datasets contain approximately 47k transitions.

\begin{table*}[!t]
\centering
\footnotesize
\caption{Dataset summary. Sizes are approximately matched at around 47k transitions.}
\label{tab:app-datasets}
\begin{tabular}{l l l p{7cm}}
\toprule
Dataset & Source policy & Size & Main characteristics \\
\midrule
\texttt{random\_matched} & Uniform random & $\approx 47$k & Broad state--action coverage, near-balanced actions, shorter episodes, higher terminal ratio, noisy trajectories. \\
\texttt{dqn\_eps010} & Trained DQN, $\epsilon\!=\!0.10$ & $\approx 47$k & Narrower support, longer episodes, lower terminal ratio, higher-return behavior, good action supervision. \\
\texttt{mixed\_random50\_dqn010} & 50--50 mix & $\approx 47$k & Intermediate raw statistics, but poor under offline Double DQN. \\
\texttt{mixed\_random20\_dqn010} & 20--80 mix & $\approx 47$k & Closer to behavior data, yet still poor with transition-level mixing. \\
\bottomrule
\end{tabular}
\end{table*}

Two high-level contrasts are the most important:
\begin{itemize}[leftmargin=1.5em]
    \item \texttt{random\_matched} provides coverage without behavior quality;
    \item \texttt{dqn\_eps010} provides behavior quality without broad support.
\end{itemize}
These opposing properties explain why the same offline dataset can favor different learning paradigms.

\section{Fixed-Point Specification}
\label{app:fixedpoint-spec}

\Cref{tab:app-fp-spec} lists the complete fixed-point specification used in all verification artifacts, defined in the \texttt{zk\_specs.py} module.

\begin{table}[!t]
\centering
\footnotesize
\caption{Fixed-point arithmetic specification.}
\label{tab:app-fp-spec}
\begin{tabular}{l l p{2.8cm}}
\toprule
Parameter & Value & Description \\
\midrule
\texttt{FP\_SCALE} & 1000 & Scaling: $\mathrm{fp}(x) = \mathrm{round}(x \cdot 1000)$ \\
\texttt{OBS\_DIM} & 4 & Observation dimension \\
\texttt{ACTION\_DIM} & 2 & Action space size \\
\texttt{GAMMA\_FP} & 990 & $\gamma = 0.99$ in fixed-point \\
\texttt{LOSS\_TYPE} & \texttt{smooth\_l1} & SmoothL1 loss \\
\texttt{SMOOTH\_L1\_BETA\_FP} & 1000 & $\beta = 1.0$ in fixed-point \\
\bottomrule
\end{tabular}
\end{table}

\section{Artifact JSON Schema}
\label{app:artifact-schema}

The repository currently uses JSON artifacts as pre-ZK verifier inputs. These artifacts are intended to clarify the statement structure before it is translated to a true proving backend. The current schema separates public inputs, witness data, and prototype-only audit metadata.

\paragraph{TD and minibatch artifacts.}
The TD artifacts contain:
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{\texttt{public}}: verifier-visible values such as \texttt{dataset\_root}, \texttt{checkpoint\_sha256}, \texttt{loss\_type}, \texttt{batch\_size}, and \texttt{batch\_loss\_fp};
    \item \textbf{\texttt{items}}: per-transition witnesses including transition data, serialized leaf values, Merkle authentication paths, and TD witnesses;
    \item \textbf{\texttt{notes}}: prototype metadata used for debugging and audit convenience.
\end{itemize}

\paragraph{One-step update artifacts.}
The one-step update artifact extends the minibatch artifact with:
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{\texttt{public}}: \texttt{pre\_checkpoint\_sha256}, \texttt{post\_checkpoint\_sha256}, \texttt{optimizer\_type}, and \texttt{learning\_rate\_fp};
    \item \textbf{\texttt{update\_witness}}: \texttt{batch\_loss\_fp}, pre/post state hashes, parameter summaries, \texttt{gradient\_tensors}, and \texttt{delta\_tensors}.
\end{itemize}
Some one-step fields, especially parameter summaries and redundant hashes, are audit-friendly prototype fields rather than finalized circuit-level fields.

\paragraph{Short-trace artifacts.}
The current B3 short-trace artifact contains:
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{\texttt{public}}: \texttt{dataset\_root}, \texttt{trace\_batch\_indices}, \texttt{num\_steps}, \texttt{batch\_size}, \texttt{loss\_type}, \texttt{optimizer\_type}, \texttt{learning\_rate\_fp}, \texttt{sampling\_rule\_type}, \texttt{start\_offset}, \texttt{target\_sync\_every}, \texttt{initial\_checkpoint\_sha256}, and \texttt{final\_checkpoint\_sha256};
    \item \textbf{\texttt{steps}}: per-step checkpoint hashes, target-sync flags, \texttt{sync\_state\_witness}, and embedded one-step artifacts;
    \item \textbf{\texttt{notes}}: an empty compatibility object after B3 cleanup.
\end{itemize}

Operational paths are no longer persistent short-trace artifact metadata. The Python verifier receives paths through runtime environment variables such as \texttt{SHORT\_TRACE\_MERKLE\_PATH}, \texttt{SHORT\_TRACE\_INITIAL\_CHECKPOINT\_PATH}, and \texttt{SHORT\_TRACE\_FINAL\_CHECKPOINT\_PATH}. Benchmark summaries may still record paths such as \texttt{final\_checkpoint\_path} for reproducibility, but those fields are benchmark metadata rather than artifact-schema fields.

\section{File Naming Conventions}
\label{app:naming}

The codebase follows a stage-oriented naming style:
\begin{itemize}[leftmargin=1.5em]
    \item \texttt{generate\_*} for data collection;
    \item \texttt{flatten\_*} for episode-to-transition conversion;
    \item \texttt{train\_*} for model training;
    \item \texttt{evaluate\_*} for checkpoint re-evaluation;
    \item \texttt{export\_*} and \texttt{verify\_*} for artifact verification; and
    \item \texttt{analyze\_*} for post-hoc analysis.
\end{itemize}

Episode datasets use the naming \texttt{<name>\_episodes.pkl} with companion \texttt{.summary.json} files. Transition-level datasets use \texttt{<name>\_transitions.pkl}.

\section{Reporting Notes}
\label{app:reporting-notes}

We distinguish two kinds of variability:
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{within-seed evaluation variance}: standard deviation over the 100 evaluation episodes for a selected checkpoint;
    \item \textbf{across-seed variance}: standard deviation across seed-wise mean returns (reported in aggregate rows).
\end{itemize}

This distinction matters because a method can be internally variable yet consistent across seeds, or vice versa.
