We presented a concrete research path toward verifiable offline DQN training from committed trajectories. Rather than attempting to solve full reinforcement-learning verifiability in a single step, we first established an offline benchmark pipeline on CartPole-v1, analyzed how dataset structure interacts with different offline learning paradigms, and then built a pre-ZK artifact/verifier prototype for the core training computations of interest.

Our empirical findings are instructive. A narrow high-return behavior dataset is highly favorable to behavior cloning, while naive offline Double DQN performs poorly on the same data. A conservative Q-learning objective substantially improves robustness in this setting, suggesting that not every offline RL pipeline is equally suitable for future verifiable-training formulations. More broadly, these experiments show that verifiability claims are meaningful only when the underlying learning computation is itself stable, reproducible, and tied to a fixed committed dataset.

On the verification side, the current prototype already supports committed-sample membership checks, Double-DQN-style Bellman target correctness, SmoothL1 TD-loss correctness, minibatch-average loss consistency, public checkpoint anchoring via SHA-256, and a stronger one-step SGD update statement including gradient recomputation, parameter-delta consistency, SGD update consistency, and target-network invariance. Beyond isolated one-step verification, the repository now also supports short verified training traces with explicit checkpoint chaining and target-network synchronization semantics. In particular, our current pre-ZK experiments successfully verify not only 2-step traces, but also longer 4-step and 8-step traces. This is an important milestone: the project has moved beyond arithmetic-level verification of a single update and now begins to verify a small but nontrivial offline training process.

At the same time, the current system remains intentionally limited. It is still a pre-ZK artifact/verifier prototype rather than a full cryptographic proof-of-training system. The present implementation does not yet provide a real zero-knowledge backend, long multi-step proof composition over realistic training horizons, replay-sampling correctness across a full run, full target-network synchronization verification over long traces, recursive proof aggregation, or proof of model-selection procedures such as best-checkpoint selection and early stopping. For this reason, the current work should be interpreted as an intermediate research milestone: substantially stronger than a toy TD-arithmetic verifier, but not yet a complete end-to-end proof-of-training construction.

\paragraph{Future work.}
The immediate next step is to continue strengthening multi-step verification beyond the current short-trace setting. This includes longer trace composition, clearer replay-sampling correctness, stronger synchronization semantics, and a more circuit-friendly witness design that can be translated into a genuine proving backend.

Beyond that, several directions remain important:
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{ZK backend integration:} translating the current fixed-point arithmetic and statement structure into an actual proving backend such as a zkSNARK system;
    \item \textbf{Longer and richer traces:} moving from short verified traces to substantially longer training prefixes with stronger process-level guarantees;
    \item \textbf{Replay-sampling verification:} proving that minibatch indices were generated according to a declared sampling rule over the committed dataset;
    \item \textbf{Larger environments:} extending beyond CartPole-v1 to environments with higher-dimensional observations and larger action spaces;
    \item \textbf{Optimizer generalization:} supporting more complex optimizers, including Adam and related adaptive methods;
    \item \textbf{Proof composition:} using recursive techniques to aggregate many verified steps into a stronger proof of training.
\end{itemize}

The next milestone is therefore not generic ``RL + ZK,'' but a stronger multi-step verifiable offline DQN training process built on committed trajectories and eventually backed by a real zero-knowledge proving system. Taken together, the current results support the broader claim of this work: offline DQN training on committed trajectories can be decomposed into meaningful verifiable statements, providing a practical path from TD arithmetic, to one-step update correctness, and further toward process-level verifiable reinforcement-learning training.