Offline reinforcement learning (offline RL) considers the setting in which a policy is learned from a fixed dataset rather than through continued online interaction with the environment. This setting is especially attractive for safety-critical or resource-constrained applications, because data collection can be separated from training and the same dataset can be reused across multiple learning procedures. At the same time, this separation creates a natural systems question: if a model is claimed to have been trained on a particular offline dataset, how can another party verify that the key training computations were actually carried out correctly?

This question becomes especially important in outsourced training, cross-organizational collaboration, and privacy-sensitive deployments. In such settings, a verifier may want confidence that the training process followed a declared specification, but should not necessarily learn the raw trajectories, rewards, or model weights. A natural cryptographic perspective is therefore to first commit the dataset, and then prove that the claimed training computations were performed correctly with respect to that committed data.

Recent work relevant to this problem comes from two largely separate directions. On one side, reinforcement-learning-related applications of zero-knowledge proofs have appeared in areas such as federated auditability, distributed RL privacy, multi-agent verification, and bandit-style decision verification. On the other side, a separate line of work has developed zero-knowledge proofs of training for committed datasets in supervised or general deep learning. However, the intersection between these two directions remains limited: there is still relatively little work on proving the correctness of RL-specific training computations on a pre-committed offline trajectory dataset.

This paper focuses on that gap through the concrete problem of \emph{zero-knowledge verifiable offline DQN training from committed trajectories}. We choose offline DQN as a first target because it is expressive enough to capture core reinforcement-learning computations while remaining structurally simpler than more complex actor--critic pipelines. In particular, offline DQN already requires verifying RL-specific operations such as Bellman target computation, TD-loss computation, and gradient-based updates, while still allowing the training process to be anchored to a fixed offline dataset.

Our goal is not to claim that we already solve full proof-of-training for offline RL. Instead, we develop the problem formulation and a sequence of increasingly strong verification statements that can serve as intermediate milestones toward that long-term objective. The current repository should therefore be understood as a \emph{pre-ZK artifact/verifier prototype} rather than a complete zero-knowledge backend. The implemented prototype already supports committed-transition membership checks, Double-DQN-style Bellman target correctness, SmoothL1 TD-loss correctness, minibatch-loss consistency, checkpoint anchoring, a stronger one-step SGD update statement, and short verified training traces.

The project also now goes beyond isolated one-step verification. On the experimental side, we evaluate short verified training traces up to 8 steps with explicit checkpoint chaining and target-network synchronization semantics. We further strengthen this short-trace setting with deterministic contiguous sampling-rule enforcement, where the verifier checks that per-step minibatch indices match a declared public rule parameterized by batch size and start offset. A negative sanity check additionally shows that the verifier rejects a tampered artifact whose public batch indices no longer match the declared sampling rule. These results do not yet constitute a full cryptographic proof of training, but they demonstrate that offline DQN training can already be decomposed into structured verifiable statements that extend beyond local arithmetic checks.

A second motivation for our formulation comes from the interaction between verifiability and meaningful learning dynamics. A training computation is only worth certifying if it is itself a meaningful and reproducible learning computation. For this reason, we do not treat the cryptographic layer in isolation. We first study the offline RL behavior of the benchmark setting and show that dataset structure matters substantially: narrow high-return behavior data is highly favorable to behavior cloning, naive offline Double DQN is weak on the same data, and conservative offline value learning is significantly more stable. These observations matter because they clarify which learning settings are worth certifying in the first place.

The main contributions of this work are as follows:

\begin{itemize}[leftmargin=1.5em]
    \item We formulate the problem of zero-knowledge verifiable offline DQN training from committed trajectories, targeting the gap between proof-of-training on committed data and RL-specific update verification.
    \item We implement a pre-ZK artifact/verifier prototype that checks committed-transition membership, Bellman target correctness, SmoothL1 TD-loss correctness, minibatch-loss consistency, and checkpoint anchoring.
    \item We extend the prototype to a stronger one-step offline DQN update statement with gradient recomputation, parameter-delta consistency, SGD update consistency, and target-network invariance.
    \item We further extend the system to short verified training traces with checkpoint chaining, target-network synchronization semantics, deterministic contiguous sampling-rule enforcement, and a negative sanity check demonstrating rejection under sampling-rule mismatch.
    \item We clean up the short-trace artifact contract so that operational filesystem paths are supplied by the runtime environment rather than stored as persistent artifact metadata.
    \item We provide experimental evidence that the current statement design scales from one-step verification to short process-level trace verification while remaining explicit about its current pre-ZK scope and limitations.
\end{itemize}

The remainder of the paper is organized as follows. We first review related work and position the problem relative to both RL+ZK systems and proof-of-training for committed datasets. We then describe the offline RL benchmark setting and the commitment pipeline used in the prototype. Next, we formalize the verification statements and artifact design, including one-step updates, short traces, and deterministic sampling-rule enforcement. We then present experimental results on both the RL side and the verification side, and conclude with current limitations and the most natural next steps toward a real zero-knowledge proving backend.
