The system does not prove a full DQN training run. It does not prove that a
final checkpoint follows from an initialization through all replay batches,
target-network synchronizations, optimizer states, or model-selection decisions.
It also does not prove Adam; the tiny update extension is scoped to simple SGD.

The current backend coverage is still uneven by design. Distinct TD has
CartPole SP1 proofs for batch sizes 1, 2, 4, and 8. Forward-TD MLP has batch-1
SP1 proofs for CartPole and MountainCar, while the CartPole batch-2 row is an
SP1 execute result rather than a proof row. Tiny one-step SGD has a batch-1 SP1
proof for a 4-8-2 CartPole network, but no batch-2 proof and no long update
trace. These rows should be described as relation-level proofs, not as full
proof-of-training evidence.

The benchmarks are small-scale. CartPole and MountainCar are classic-control
tasks, and MountainCar uses a random-policy transition dataset for the second
environment artifact. These choices are appropriate for proving relation
correctness and reproducibility, but they are not evidence of large-scale RL
training performance.

The commitment layer starts after data collection. A verifier can check that a
revealed transition belongs to the committed replay set, but not that the replay
set was collected honestly or that it covers a desired behavior distribution.
The Python verifier path also reveals or processes witness data directly and
therefore should not be treated as a privacy-preserving verifier.

Finally, the SP1 proof cost is still prototype-scale. Verification is fast, but
proving takes minutes for the reported cases. Scaling to practical
proof-of-update or proof-of-training will require more efficient neural-network
proofs, aggregation or recursion over repeated updates, and careful treatment
of optimizer and sampling semantics.
