We consider a discounted Markov decision process with state space $\states$, action space $\actions$, reward function $r$, and discount factor $\gamma \in [0,1)$. Our experimental environment is CartPole-v1~\cite{brockman2016gym}, which has low-dimensional continuous observations and a discrete action space of size two.

\paragraph{Committed offline dataset.}
Instead of learning from online interaction, we assume a fixed trajectory dataset is collected first and then transformed into a transition dataset
\[
\dataset = \{(s_i, a_i, r_i, s'_i, d_i)\}_{i=1}^N,
\]
where $d_i \in \{0,1\}$ indicates whether the transition is terminal. In the eventual verifiable setting, the dataset will be committed before training via a Merkle tree~\cite{merkle1987}, and all claimed computations must be shown to be consistent with that commitment.

\paragraph{Offline value learning.}
Given $\dataset$, the learning objective is to estimate an action-value function $Q_\theta(s,a)$~\cite{watkins1992qlearning} without further environment interaction. For DQN-style training~\cite{mnih2015dqn}, the Bellman target for a transition is
\[
y_i = r_i + \gamma (1-d_i) \max_{a' \in \actions} Q_{\bar{\theta}}(s'_i, a'),
\]
or, in Double DQN form~\cite{hasselt2016double},
\begin{align*}
y_i &= r_i + \gamma (1-d_i) \\
&\quad \times Q_{\bar{\theta}}\!\left(s'_i, \arg\max_{a' \in \actions} Q_\theta(s'_i, a')\right),
\end{align*}
where $\bar{\theta}$ denotes target network parameters.

The TD loss over a minibatch $B$ is
\[
\mathcal{L}_{\mathrm{TD}}(\theta; B)
=
\frac{1}{|B|}
\sum_{i \in B}
\ell\big(Q_\theta(s_i,a_i), y_i\big),
\]
where $\ell$ is Huber loss (SmoothL1)~\cite{huber1964robust}, defined as
\[
\ell(x, y) = \begin{cases}
\frac{(x-y)^2}{2\beta} & \text{if } |x-y| < \beta, \\
|x-y| - \frac{\beta}{2} & \text{otherwise,}
\end{cases}
\]
with $\beta = 1.0$ in our implementation.

\paragraph{Behavior cloning.}
For comparison, we also study behavior cloning (BC), which treats the offline dataset as supervised state--action pairs and learns a policy $\pi_\phi(a\mid s)$ by minimizing cross-entropy against the dataset actions. BC does not bootstrap through learned value targets and therefore serves as a useful reference point for understanding whether dataset failures are due to data quality or to offline temporal-difference learning itself.

\paragraph{Conservative offline RL.}
To bridge the gap between imitation and naive offline Q-learning, we evaluate a discrete conservative Q-learning variant~\cite{kumar2020cql}. In addition to the TD term, it penalizes large Q-values on actions not supported by the data through a regularizer of the form
\begin{align*}
\mathcal{L}_{\mathrm{CQL}}(\theta; B)
&=
\mathcal{L}_{\mathrm{TD}}(\theta; B)
+
\alpha \Bigg(
\log \sum_{a \in \actions} e^{Q_\theta(s,a)} \\
&\quad -
Q_\theta(s,a_{\mathrm{data}})
\Bigg),
\end{align*}
where $\alpha > 0$ controls conservatism.

\paragraph{Goal of verifiability.}
Our long-term goal is not merely to train offline RL from fixed data, but to prove that specific training computations were correctly carried out over a committed dataset. In this work, we therefore treat the offline RL benchmark as the foundation upon which future proof statements will be built.