\paragraph{Offline RL and DQN.}
DQN showed that deep value functions can learn control policies through
temporal-difference learning with experience replay and a target
network~\cite{mnih2015dqn,watkins1992qlearning}. Double DQN refines this
structure by using the online network for next-action selection and the target
network for value evaluation~\cite{hasselt2016double}. Offline RL studies the
more constrained setting in which training uses a fixed dataset and no further
environment interaction~\cite{levine2020offline}. This fixed-data setting is
natural for commitment-based verification, but it also makes value learning
fragile under distribution shift~\cite{fujimoto2019offpolicy}. Conservative
Q-Learning addresses this by regularizing value estimates for unsupported
actions~\cite{kumar2020cql}. Our work does not propose a new offline RL
algorithm. Instead, it asks how the TD computations used by offline DQN-style
training can be made verifiable over committed trajectories.

\paragraph{Proof-of-learning and proof-of-training.}
Proof-of-Learning introduced the problem of proving that released model
parameters resulted from an expensive training procedure
~\cite{jia2021proofoflearning}. Later zero-knowledge proof-of-training work
aims to prove correct training on committed data without revealing private data
or model parameters~\cite{zkdl2023,zkpotvicinity2025}. These systems primarily
target supervised or general deep learning training. They motivate our threat
model, but they do not directly address RL-specific semantics such as terminal
Bellman branches, target-network values, replay membership, and TD losses. Our
scope is therefore complementary: we do not prove all DQN training; we prove a
smaller RL-specific TD relation that can be embedded later into a fuller update
or trace proof.

\paragraph{Verifiable and zero-knowledge machine learning.}
Verifiable ML systems have focused heavily on inference correctness. SafetyNets
develops interactive proofs for neural-network inference on untrusted
clouds~\cite{safetynets2017}. zkCNN gives zero-knowledge proofs for CNN
prediction and accuracy while hiding model information~\cite{zkcnn2021}. VeriML
uses SNARKs to provide integrity and fair-payment assurances for outsourced ML
tasks~\cite{veriml2021}. Recent ZKML surveys organize this literature into
verifiable inference, testing, and training~\cite{zkmlsurvey2026}. Our work
differs in the computation being proved: the first-class statement is not a
classification output or ordinary supervised update, but the TD computation
that links a committed transition to a Bellman target and SmoothL1 loss.

\paragraph{Zero-knowledge proof systems and zkVMs.}
Modern zero-knowledge systems enable succinct verification of general
computation, with constructions such as Groth16 and PLONK providing important
building blocks~\cite{groth2016zksnark,gabizon2019plonk}. zkVMs trade some
constraint-level specialization for developer ergonomics by proving execution
of programs written in conventional languages. SP1 is a Rust-oriented zkVM that
proves execution of Rust or LLVM-compiled programs~\cite{succinct2024sp1}. We
use SP1 because the TD MVP relation involves hashing, Merkle paths, branching,
schema checks, and fixed-point integer arithmetic; implementing the first
backend in a zkVM is substantially more direct than hand-writing a circuit
before the relation stabilizes.

\paragraph{Verifiable RL.}
Prior verifiable RL work often focuses on interpretable or formally verifiable
policies, rather than cryptographic verification of training computations.
Programmatic-policy approaches, for example, search for policies that can be
checked by symbolic methods~\cite{verma2019verifiable}. Other recent work
combines zero-knowledge tools with distributed or federated RL primarily for
privacy, communication integrity, or aggregation security. These directions are
valuable, but they leave a gap around cryptographic correctness of the
RL-specific arithmetic inside offline value learning. Our contribution targets
that gap at the TD/minibatch-TD layer over committed trajectories.
