\subsection{Python Regression}

The locked Python regression contains eleven checks and passes all of them:

\begin{table}[!t]
\centering
\small
\caption{Locked Python regression status.}
\label{tab:python-regression}
\begin{tabular}{lc}
\toprule
Check group & Status \\
\midrule
Compile checks & pass \\
TD/minibatch artifact verifier & pass \\
Forward TD consistency verifier & pass \\
One-step update verifier & pass \\
Short-trace contiguous verifier & pass \\
Short-trace seeded verifier & pass \\
One-step negative tests & pass \\
Short-trace negative tests & pass \\
Minibatch TD negative tests & pass \\
Distinct TD-1/2/4/8 Python-only benchmark & pass \\
TD MVP test-vector negative tests & pass \\
\bottomrule
\end{tabular}
\end{table}

This regression matters because the Python verifier is the semantic oracle used
to cross-check the SP1 backend. The SP1 result is therefore not evaluated in
isolation: accepted and rejected TD fixtures are checked against the same
reference semantics.

\subsection{SP1 Proof Benchmark}

\Cref{tab:sp1-proof-benchmark} reports the locked historical SP1 proof
benchmark. The full run was generated on Kaggle at 2026-05-12T12:37:34Z with
\texttt{benchmark\_sp1\_td\_mvp.py --prove}. Phase A replaces this runner as the
main paper-facing path with \texttt{benchmark\_distinct\_td\_sp1.py}, which uses
distinct committed replay transitions and public ordered leaf indices. The
distinct runner currently passes Python-only TD-1/2/4/8 smoke tests locally;
SP1 proof refresh should be rerun on Linux/WSL/Kaggle before freezing this table.

\begin{table*}[!t]
\centering
\small
\caption{Historical SP1 TD MVP proof benchmark before Phase A distinct-batch
refresh. TD-1 proves one committed transition and TD arithmetic. TD-2/4/8 prove
minibatch membership, per-item TD arithmetic, and public integer batch-average
loss.}
\label{tab:sp1-proof-benchmark}
\begin{tabular}{l l c r r r r}
\toprule
Case & Relation & Batch & Prove (s) & Verify (s) & Proof bytes & Cycles \\
\midrule
TD-1 & Merkle + TD + SmoothL1 & 1 & 142.324547 & 0.157464 & 2782625 & 382915 \\
TD-2 & Merkle + TD + SmoothL1 + avg. loss & 2 & 154.923089 & 0.157712 & 2787687 & 725309 \\
TD-4 & Merkle + TD + SmoothL1 + avg. loss & 4 & 188.501940 & 0.155969 & 2795631 & 1425790 \\
TD-8 & Merkle + TD + SmoothL1 + avg. loss & 8 & 275.077262 & 0.157424 & 2812327 & 2834727 \\
\bottomrule
\end{tabular}
\end{table*}

The results show two useful properties. First, proof size grows slowly across
the tested minibatch sizes, from 2.78 MB at TD-1 to 2.81 MB at TD-8. Second,
verification time remains approximately constant at 0.16 seconds. Proving time
and cycle count increase with batch size, as expected, because each additional
item adds another membership and TD check.

\subsection{Python/SP1 Agreement and Tamper Rejection}

The benchmark runner reports:
\begin{verbatim}
all_python_expected = True
all_sp1_expected = True
python_sp1_agreement = True
\end{verbatim}
The standalone SP1 negative suite also reports:
\begin{verbatim}
all_sp1_negative_cases_passed = true
\end{verbatim}

\Cref{tab:tamper-summary} summarizes the adversarial coverage. For each case,
the expected outcome is rejection; Python and SP1 agree.

\begin{table*}[!t]
\centering
\small
\caption{Tamper rejection summary. Each tampered case is rejected by the Python
semantic oracle and by SP1 execution.}
\label{tab:tamper-summary}
\begin{tabular}{p{4.2cm} p{9.8cm}}
\toprule
Group & Rejected cases \\
\midrule
Schema and fixed-point semantics &
schema version, fixed-point rounding, terminal/non-terminal done branch \\
Transition and commitment &
reward, observation, leaf encoding, leaf hash, Merkle sibling, leaf index, path order \\
TD witness and public claims &
target-network value, claimed target, claimed loss, TD error \\
Batch aggregation &
claimed batch loss, public batch size, item loss, item index, duplicate index, swapped item order, batch path order, batch target value, batch rounding \\
\bottomrule
\end{tabular}
\end{table*}

These negative tests are not a substitute for a formal security proof of the
entire system, but they are important engineering evidence. They show that the
backend is checking the intended relation rather than accepting arbitrary
well-formed JSON or trusting host-side prechecks.

\subsection{Pre-ZK One-Step and Short-Trace Context}

The Python extension layer verifies a one-step SGD update artifact and an
8-step short trace with checkpoint chaining, target-network synchronization,
and deterministic contiguous sampling-rule enforcement. The locked short-trace
benchmark uses 8 update steps, target synchronization every two steps, and
batch sizes 4 or 8. Representative verification times are 13.48 s, 13.64 s,
and 14.02 s for the three locked 8-step runs.

These results are reported only as context. They support the claim that the
artifact design has a plausible path from TD proofs toward update and trace
proofs. They do not change the cryptographic claim of this paper, which is
limited to the SP1 TD/minibatch-TD backend.

\subsection{Offline RL Context}

The repository also contains offline RL baseline results on the committed-style
\texttt{dqn\_eps010} dataset. Naive offline Double DQN is weak on this narrow
behavior dataset, while behavior cloning and CQL-lite are much stronger. The
aggregate 100-episode returns are 60.14 for naive offline Double DQN, 417.65
for behavior cloning, and 401.78 for CQL-lite. This observation is not the
central contribution, but it motivates why future proof-of-update work should
focus on learning rules that are empirically meaningful in the offline regime.
