The backend lives under \path{zk_backend/td_mvp/sp1/} and follows the standard
host/guest/shared split. The shared crate defines typed public inputs, private
witnesses, Merkle steps, model layers, fixed-point helpers, SHA-256 hashing, TD
arithmetic, MLP forward checks, and update checks. The guest reads a typed input
and calls the shared verifier. The host loads JSON fixtures, selects execution
or proof mode, optionally disables host prechecks for tamper cases, verifies
proofs for accepted cases, and records metrics.

The distinct TD relation proves membership and arithmetic over ordered replay
minibatches. For each item, the guest recomputes the leaf, leaf hash, Merkle
root, terminal branch, target, TD error, and SmoothL1 loss. It rejects duplicate
indices when the public batch mode is distinct, rejects reordered items against
the public leaf-index list, and checks the public integer batch-average loss.

The forward-TD MLP relation adds model-grounded Q-values. The witness contains
quantized online and target model weights plus intermediate activations and
ReLU masks. The relation hashes model weights to public commitments, evaluates
the online network on $s$ and $s'$, evaluates the target network on $s'$,
selects the online argmax action, reads the corresponding target value, and
then runs the same Bellman and SmoothL1 checks as TD.

The tiny one-step SGD relation checks a one-item, small-network SGD update with
public pre/post model commitments and private gradient/delta tensors. The SP1
guest checks the forward-TD subrelation, the SmoothL1 derivative branch,
gradient and delta tensors, the fixed-point SGD update equation, and the post
model commitment. The current proof is intentionally micro-scale: batch 1,
network 4-8-2, SGD only, and no long trace or Adam state.
