The prover holds private replay transitions, private model weights, and
intermediate witnesses. The verifier knows public commitments and public claims:
the dataset root, fixed-point scale, discount factor, loss type, relation id,
batch indices, model commitments when the relation includes models, and claimed
per-item or batch losses.

The dishonest prover may try to make a false public claim by changing a replay
transition, substituting a Merkle path, reordering minibatch items, using the
wrong terminal branch, altering fixed-point rounding, changing model weights
after committing to them, lying about activations or ReLU masks, changing the
argmax action, altering selected target Q-values, or submitting inconsistent
gradient/update tensors. The verifier's goal is to accept only when the
relation-specific witness satisfies the public statement.

The system provides relation-level integrity. For the TD MVP SP1 backend, the
verifier relies on the soundness of the SP1 proof system and on collision
resistance of SHA-256 for the Merkle commitment. For Python-only extension
relations, the verifier receives deterministic semantic-check evidence but not
a zero-knowledge proof. The paper marks these cases explicitly in the
evaluation tables.

The threat model excludes several larger claims. It does not prove that replay
data were collected honestly before commitment, that the committed dataset is
representative, that a final policy is performant or safe, or that a full
checkpoint was produced by an entire DQN training run. It also does not make a
privacy claim for the Python verifier path.
